NGO analysis

### 2022-07-22 Shiny/Test/Flexdashboard rows.Rmd
Updating to use observe() |> bindEvent(). Added function to create a maximum value for the revenue and expenses plots. Adding this to the y limits for these plots.
Many tests in the Facet test document.

### Information 1

@@

### Information 2
```{r}

@@

```{r shiny, include=FALSE}
# Shiny actions
observeEvent(input$click, { # wait for button click

  #---- Data frames --------------------------------------------------------------      
  # creating data frame from html file
  htmldata <- reactive({
    read_proff8(
      input$html$datapath,
      as.character(input$start), as.character(input$end)
    )
  })

@@

  #---- Value Boxes --------------------------------------------------------------

  # Creating Fundraising ROI value
  KPI_fundraising_num <- reactive({
    exceldata() |>
      # most recent year
      filter(year == max(year)) |>
      transmute(
        # Calculating the value as a percentage; removing all other
        KPI_fundraising_num =
          (revenue_private_contributions +
            revenue_membership_fees - expenses_fundraising) /
            expenses_fundraising * 100
      ) |>
      # just want the single number
      pull()
  })

@@

  #----Expenses---------------------------------------
  expenses_plot <- reactive({
    exceldata() |>
      # Renaming for the purposes of the plot + dropping other variables
      transmute(
        Year = as.factor(year),
        Other = expenses_other,
        Administrative = expenses_administrative,
        Fundraising = expenses_fundraising,
        `Program services` = expenses_program_services
      ) |>
      # Pivoting to use fill
      pivot_longer(c(Other:`Program services`), names_to = "Expenses") |>
      # Ordering for the plot
      mutate(
        Expenses = ordered(Expenses,
          levels =
            c("Program services", "Other", "Fundraising", "Administrative")
        )
      ) |>
      ggplot(aes(Year, value, fill = Expenses)) +
      geom_col() +
      scale_y_continuous(labels = label_dollar(prefix = "NOK ")) +
      scale_fill_met_d("Hokusai2") +
      labs(x = "", y = "", title = "Expenses (in thousands)")
  })

@@

  #----Revenue------------------------------------------
  revenue_plot <- reactive({
    exceldata() |> 
      # Renaming for the purposes of the plot + dropping other variables
      transmute(
        Year                    = as.factor(year),
        `Private contributions` = revenue_private_contributions,
        `Membership fees`       = revenue_membership_fees,
        `Public grants`         = revenue_public_grants,
        Investments             = revenue_investments,
        `Operational activities`= revenue_operational_activities,
        `Commercial activities` = revenue_commercial_activities,
        Other                   = revenue_other
      ) |> 
      # Pivoting to use fill
      pivot_longer(
        c(`Private contributions`:Other), names_to = "Revenue source"
      ) |> 
      ggplot(aes(Year, value, fill = `Revenue source`)) +
      geom_col() +
      scale_y_continuous(labels = label_dollar(prefix = "NOK ")) +
      scale_fill_manual(values = met.brewer("Hokusai2", 7)) +
      labs(x = "", y = "", title = "Revenue (in thousands)")
  })

@@

  # Reactive function with slightly nicer colours + ensuring positive values are
  # always green
  scale_fill_green <- reactive({
    scale_fill_met_d("Tsimshian",
      direction = ifelse(
        mean(htmldata()$balance_positive,
          na.rm = TRUE
        ) == 1, -1, 1
      )
    )
  })
})

@@

# Function to turn KPI values into NA or percentage string
KPI_to_string <- function(variable){
  # Returning NA if the KPI is Inf (division by zero) or NA, to avoid
  # layout-breaking errors, otherwise formatting
  if (is.na(variable)) {
    NA
  } else if (variable == Inf) {
    NA
  } else {
    # Shortening (lengthening) the value, adding %
    str_c(format(variable, digits = 3), "%")
  }
}
```

>>>>

### Key Performance Indicators

@@

### Plots
```{r}

@@

```{r shiny, include=FALSE}
# Shiny actions
observe({ # wait for button click

  #---- Data frames ------------------------------------------------------------      
  # creating data frame from html file
  htmldata <- reactive({
    read_proff8(
      input$html$datapath,
      as.character(input$start), as.character(input$end)
    )
  })

@@

  #---- Value Boxes ------------------------------------------------------------

  # Creating Fundraising ROI value
  KPI_fundraising_num <- reactive({
    exceldata() |>
      # most recent year
      filter(year == max(year)) |>
      transmute(
        # Calculating the value as a percentage; removing all other
        KPI_fundraising_num =
          (revenue_private_contributions +
            revenue_membership_fees - expenses_fundraising) /
            expenses_fundraising * 100
      ) |>
      # just want the single number
      pull() |> 
      first()
  })

@@

  #----Expenses---------------------------------------
  expenses_plot <- reactive({
    exceldata() |>
      # Renaming for the purposes of the plot + dropping other variables
      transmute(
        Year = as.factor(year),
        Other = expenses_other,
        Administrative = expenses_administrative,
        Fundraising = expenses_fundraising,
        `Program services` = expenses_program_services
      ) |>
      # Pivoting to use fill
      pivot_longer(c(Other:`Program services`), names_to = "Expenses") |>
      # Ordering for the plot
      mutate(
        Expenses = ordered(Expenses,
          levels =
            c("Program services", "Other", "Fundraising", "Administrative")
        )
      ) |>
      ggplot(aes(Year, value, fill = Expenses)) +
      geom_col() +
      scale_y_continuous(labels = label_dollar(prefix = "NOK "),
                         limits = c(NA, maximum())) +
      scale_fill_met_d("Hokusai2") +
      labs(x = "", y = "", title = "Expenses (in thousands)")
  })

@@

  #----Revenue------------------------------------------
  revenue_plot <- reactive({
    exceldata() |> 
      # Renaming for the purposes of the plot + dropping other variables
      transmute(
        Year                    = as.factor(year),
        `Private contributions` = revenue_private_contributions,
        `Membership fees`       = revenue_membership_fees,
        `Public grants`         = revenue_public_grants,
        Investments             = revenue_investments,
        `Operational activities`= revenue_operational_activities,
        `Commercial activities` = revenue_commercial_activities,
        Other                   = revenue_other
      ) |> 
      # Pivoting to use fill
      pivot_longer(
        c(`Private contributions`:Other), names_to = "Revenue source"
      ) |> 
      ggplot(aes(Year, value, fill = `Revenue source`)) +
      geom_col() +
      scale_y_continuous(labels = label_dollar(prefix = "NOK "),
                         limits = c(NA, maximum())) +
      scale_fill_manual(values = met.brewer("Hokusai2", 7)) +
      labs(x = "", y = "", title = "Revenue (in thousands)")
  })

@@

  # Reactive function with slightly nicer colours + ensuring positive values are
  # always green
  scale_fill_green <- reactive({
    scale_fill_met_d("Tsimshian",
      direction = ifelse(
        mean(htmldata()$balance_positive,
          na.rm = TRUE
        ) == 1, -1, 1
      )
    )
  })

  # Reactive function to create the maximum value for revenue and expenses plots
  maximum <- reactive({
    read_excel(input$excel$datapath) |>
      select(-Firm, -`Sub-category`) |>
      filter(Category == "Revenue" | Category == "Expenses") |>
      group_by(Year, Category) |>
      summarise(
        sum = sum(Value, na.rm = TRUE)
      ) |>
      pull() |>
      max()
  })
}) |> bindEvent(input$click)

@@

# Function to turn KPI values into NA or percentage string
KPI_to_string <- function(variable){
  # Returning NA if the KPI is Inf (division by zero) or NA, to avoid
  # layout-breaking errors, otherwise formatting
  if (is.na(variable)) {
    NA
  } else if (variable == Inf) {
    NA
  } else {
    # Shortening (lengthening) the value, adding %
    str_c(format(variable, digits = 3), "%")
  }
}

?observeEvent
```
